GBM recurrence - Shotgun proteomics analysis

### 2023-02-14 reports/gbm_recurrence_general_proteomics_manuscript_report.qmd
proteomics report add toc

---
title: "GBM recurrence - Shotgun proteomics analysis"
author: "Miguel Cosenza-Contreras"
format:
  gfm: 
    toc-depth: 4 # default is 3
    number-sections: true
    execute:
      output: true
always_allow_html: true
editor: visual
---

>>>>

---
title: "GBM recurrence - Shotgun proteomics analysis"
author: "Miguel Cosenza-Contreras"
format:
  gfm:
    toc: true 
    toc-depth: 4 # default is 3
    number-sections: true
    execute:
      output: true
always_allow_html: true
editor: source
---
